%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Frontend Developer} % Job title
    {Swisslinx} % Organization
    {Zürich, Switzerland} % Location
    {Oct. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the trading platform for one of the largest Swiss banks}
        \item {Creating responsive and accessible React components based on company style guide}
        \item {Improving the tooling, development stack and development experience by including the latest technologies like react-create-app, Babel, Jest, CSS Grid}
        \item {Providing help and trainings for developers in CSS and HTML}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Frontend Developer} % Job title
    {EPAM} % Organization
    {Budapest, Hungary - Zürich, Switzerland} % Location
    {Jun. 2016 – Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created company wide used responsive and accessible React components based on company style guide for one of the largest Swiss banks}
        \item {Designed and implemented a robust platform for client advisers and relationship managers}
        \item {Handled the collaboration between teems in open-source manner}
        \item {Ramped-up newcomers and did technical interviews}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Web Developer} % Job title
    {Planorama} % Organization
    {Budapest, Hungary} % Location
    {Jan. 2016 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on planogram automation platform for retailers build on micro-services architecture}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Elastic Wings} % Organization
    {Budapest, Hungary} % Location
    {Jul. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a micro-service based, highly scalable web-shop for clothing and accessories}
        \item {Introduced Selenium based end-to-end testing}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Web Developer} % Job title
    {Hotels.com} % Organization
    {Budapest, Hungary} % Location
    {Jul. 2013 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed the architecture and developed from scratch the checkout page of mainstream global online hotel booking website}
        \item {Introduced credit card and Google Wallet as payment systems for the site}
        \item {Introduced test driven development and increased the unit test coverage by 80\%}
        \item {Trained two newcomer developers}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Web Developer} % Job title
    {R\&R Software} % Organization
    {Budapest, Hungary} % Location
    {Nov. 2012 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a billing system for banking, telecommunication and public provider companies}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {R-NET} % Organization
    {Budapest, Hungary} % Location
    {Oct. 2004 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an administration platform for Hungarian ministry of rural development}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
